A Comparative Study of Game-Theoretic and Reinforcement Learning Approaches for Jam-Resilient Wireless Networks in IoT

### 2025-05-25 paper/main.tex
Progressss

\author{
  \IEEEauthorblockN{Muhammad Umar Yaksambi}
  \IEEEauthorblockA{
    Department of Computer Science (Data Sciences)\\
    RV College Of Engineering\\
    Bengaluru, India\\
    Email: umaryaksambi@gmail.com
  }
  \and
  \IEEEauthorblockN{Anuj Devpura}
  \IEEEauthorblockA{
    Department of Computer Science (Data Sciences)\\
    RV College Of Engineering\\
    Bengaluru, India\\
    Email: anujdevpura@gmail.com
  }
  \and
  \IEEEauthorblockN{Sadashiv Todakar}
  \IEEEauthorblockA{
    Department of Computer Science (Data Sciences)\\
    RV College Of Engineering\\
    Bengaluru, India\\
    Email: sadashivtodakar@gmail.com
  }
}

>>>>

\author{
  \IEEEauthorblockN{Muhammad Umar Yaksambi}
  \IEEEauthorblockA{
    Dept. of CSE (Data Sciences)\\
    RV College Of Engineering\\
    Bengaluru, India\\
    Email: umaryaksambi@gmail.com
  }
  \and
  \IEEEauthorblockN{Anuj Devapura}
  \IEEEauthorblockA{
    Dept. of CSE (Data Sciences)\\
    RV College Of Engineering\\
    Bengaluru, India\\
    Email: anujdevapura@gmail.com
  }
  \and
  \IEEEauthorblockN{Sadashiv Todakar}
  \IEEEauthorblockA{
    Dept. of CSE (Data Sciences)\\
    RV College Of Engineering\\
    Bengaluru, India\\
    Email: sadashivtodakar@gmail.com
  }
}
